Processing simulation output

### 2020-07-29 results/README.Rmd
update 29-07 corrections

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rjson)
library(tidyverse)
library(knitr)
library(flextable)
library(officer)
```

@@

Compute standarad deviation from the 15 separate trials.
```{r}
# compute standard deviation (bootstrapped)
sdruns <- 
  runs %>%
  select(dataset, model, wss.95, rrf.10, loss) %>% 
  group_by(model, dataset) %>%
  summarise(sdwss.95 = sd(wss.95),
            sdrrf.10 = sd(rrf.10),
            sdloss = sd(loss))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rjson)
library(tidyverse)
library(knitr)
library(flextable)
library(officer)

set.seed(42)
```

@@

Compute standarad deviation from the 15 separate trials.
```{r}
# compute standard deviation (bootstrapped)
sdruns <- 
  runs %>%
  select(dataset, model, wss.95, rrf.10, loss) %>% 
  group_by(model, dataset) %>%
  summarise(sdwss.95 = sd(wss.95),
            sdrrf.10 = sd(rrf.10),
            sdloss = sd(loss))
library(boot)
# but now boostrap
sdruns <- 
  runs %>%
  select(dataset, model, wss.95, rrf.10, loss) %>% 
  group_by(model, dataset)

test <- sdruns %>% 
  ungroup()%>%
  filter(dataset == "ace", model == "NB + TF-IDF")

samplemean <- function(x, d) {
  result <- c(mean(x[1,d]), mean(x[2,d]), mean(x[3,d]))
  return(result)
}

test <- tibble(test %>% select(wss.95, rrf.10, loss))

bs <- boot(t(test),statistic = samplemean, R = 1000)

bs# standard deviation 
sd(bs$t[,1])
